Project Report\\\textsc{DEVS Ex Machina}

### 2015-04-25 manual/projectrapport.tex
* added very minimal explanation for dynamic structured to project report functional requirements

\documentclass[8pt,a4paper]{report}
\usepackage[latin1]{inputenc}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[scaled]{beramono}
\newcommand\Small{\fontsize{9}{9.2}\selectfont}
\newcommand*\LSTfont{\Small\ttfamily\SetTracking{encoding=*}{-60}\lsstyle}
\usepackage{url}
  \lstset{basicstyle=\ttfamily\tiny\color{blue}}
\usepackage{graphicx}
\usepackage[]{algorithm2e}

@@

\section{Tracing}
The tracing uses template programming, and is largely asynchronous w.r.t. the simulator kernels. This can be seen by the high utilization values when benchmarking the examples.
%TODO Stijn

@@

\chapter{Functional requirements}
\section{DEVS Formalisms}
\section{Single core}
The single core implementations follow exactly the runtime behaviour shown by the PyPDEVS simulator. We've chosen to emulate the Select() function with an integer priority value the user can set. This saves 1 virtual function call per transition and can quite easily be optimized by the compiler since it remains constant.
\subsection{DirectConnect}
%TODO Stijn/Matthijs Directconnect : what is rootmodel, only atomics in core.
\subsection{Dynamic Structured}
This is implemented but removing models is not yet fully tested.
%TODO Stijn
\subsection{Parallel}
\subsubsection{Optimistic}
Optimistic time synchronization requires an implementation of timewarp, and more extensive locking than would be required for conservative. The GVT algorithm (Mattern \cite{Mattern}) runs on a separate thread from the simulation kernel threads, so care must be taken that they don't deadlock, but don't race either.
\subsubsection{Conservative}
Conservative time synchronization is still under development.

>>>>

\documentclass[8pt,a4paper]{report}
\usepackage{hyperref}
\usepackage[latin1]{inputenc}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[scaled]{beramono}
\newcommand\Small{\fontsize{9}{9.2}\selectfont}
\newcommand*\LSTfont{\Small\ttfamily\SetTracking{encoding=*}{-60}\lsstyle}
\usepackage{url}
  \lstset{basicstyle=\ttfamily\tiny\color{blue}}
\usepackage{graphicx}
\usepackage[]{algorithm2e}

@@

\section{Tracing}
The tracing uses template programming, and is largely asynchronous w.r.t. the simulator kernels. This can be seen by the high utilization values when benchmarking the examples.
The tracing component makes heavy use of template programming. For more detailed information, please refer to \href{run:./tracersReport.pdf}{tracersReport.pdf}.

@@

\chapter{Functional requirements}
\section{DEVS Formalisms}
\section{Single core}
The single core implementations follow exactly the runtime behaviour shown by the PyPDEVS simulator. We've chosen to emulate the Select() function with an integer priority value the user can set. This saves 1 virtual function call per transition and can quite easily be optimized by the compiler since it remains constant.
\subsection{DirectConnect}
%TODO Stijn/Matthijs Directconnect : what is rootmodel, only atomics in core.
\subsection{Dynamic Structured}
Only the removal/addition of connections is currently supported. Unlike the PyPDEVS, we will try to keep a removed model intact when it is removed from the simulation.
\subsection{Parallel}
\subsubsection{Optimistic}
Optimistic time synchronization requires an implementation of timewarp, and more extensive locking than would be required for conservative. The GVT algorithm (Mattern \cite{Mattern}) runs on a separate thread from the simulation kernel threads, so care must be taken that they don't deadlock, but don't race either.
\subsubsection{Conservative}
Conservative time synchronization is still under development.
